---
title: "final-assignment"
author: "Eray Ferah"
date: "28 05 2022"
output:
word_document: default
html_document:
df_print: paged
editor_options: 
  markdown: 
    wrap: sentence
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r technical details for the analysis, echo = FALSE}
library(ggplot2)
library(lmtest)
library(scales)
library(lubridate)
library(stargazer)
library(readxl)

setwd("C:\\Users\\erayf\\Desktop\\DataScience\\Repo\\hypotheses-testing-in-econometric\\data")

# Import data
df_dis <- read_excel("disney.xlsx")
df_dis <- as.data.frame(df_dis)

######define date
df_dis$Date <- as.Date(paste(df_dis$date, 1), "%Ym%m %d")

```

```{r Calculate returns, echo = FALSE}
##### Calculate returns #####

df_dis$Return <- 0

for(i in c(2:nrow(df_dis))){
  df_dis$Return[i] <- (df_dis$disney[i]-df_dis$disney[i-1])/df_dis$disney[i-1]*100
}

```

```{r ,echo = FALSE}

df_dis$Excess_Returns <- df_dis$Return - df_dis$rf

##### Regress the basic model (no robust se) #####
# library(lmtest)
Model_1_dis <- lm(Excess_Returns ~
                mktrf
              , data=df_dis
              , na.action=na.exclude)
coeftest(Model_1_dis)
stargazer(Model_1_dis, type="text")

##### Save residuals #####
df_dis$e_1 <- residuals(Model_1_dis)

#################################################4.5.

resid1 <- df_dis$e_1
h1 <- hist(resid1)
h1

```

I have built CAPM Model with Disney stock excess return and mktrf.

Below I will be doing hypothesis testing for intercept and independent variable (t-tests)

## t-tests;

## (1) intercept coefficient = 0.

## (2) mktrf coefficient = 1.

```{r t-tests}
library(car)
library(lmtest)
library(dplyr)
library(strucchange)

##### Project 1: Hypothesis testing #####
# show t test for a=0 b=0 c=0
summary(Model_1_dis)$coefficients

# Test a=0 with t test
Model_1_dis$coefficients[1]/sqrt(diag(vcov(Model_1_dis)))[1]
linearHypothesis(Model_1_dis, c("(Intercept)=0"))

# Test b=1 with t test
linearHypothesis(Model_1_dis, c("mktrf=1"))
```

Null hypothesis, that intercept coefficient is 0, is failed to be rejected (p-value 0.2469).

Null hypothesis, that mktrf coefficient is 1, is rejected at 5 % significance level (p-value 0.02859)

## F Test that intercept coefficient is 0 and indep variable coefficient is 1.

```{r f-test}
# Test a=0 and b=1 with f test
linearHypothesis(Model_1_dis, c("(Intercept)=0", "mktrf=1"))

```

We reject the null hypothesis that intercept coefficient is 0 and mktrf's coefficient is 1 at 5 % significance level.
(p-value 0.02808).

# Diagnostic Tests

## Linearity test

```{r linearity test}
# Test for linearity of the Model using the RAMSEY reset test
resettest(Model_1_dis, power=2:4, type="fitted")

```

According to the RESET test (null hypothesis is that model is not suffering omitted variable problem), model is linear (p-value 0.4784).

## Autocorrelation test

```{r autocorrelation test}

dwtest(Model_1_dis)

```

According to Durbin-Watson test, the null hypothesis that autocorrelation of residuals is 0 and p-value is 0.932.
So we fail to reject null hypothesis and say that there is no auto correlation among residuals.

## Heteroscedasticity test

```{r Heteroscedasticity test}

bptest(Model_1_dis, ~ I(mktrf^2), data = df_dis)

```

According to white-test, which null hypothesis homoscedasticity is present, our model is homoscedastic.
p-value 0.2154

## Normality test

```{r Normality test}
library(tseries)

jarque.bera.test(resid1)

```

According to jarque bera test, the null hypothesis normality, residuals are normally distributed.
p-value 2.2e-16

## Multicollinearity test

Since CAPM model is simple linear regression (1 independent variable), there is no need for multicollinearity test.
However, if there has been more than 1 independent variable we should check a correlation matrix amon independent variables.

## Endogeneity test

Hausman test should be used to check if there is endogenity (correlation between error term and regressors).

```{r Endogeneity test}
library(plm)

model_dis <- Excess_Returns ~ mktrf

#phtest(plm(model_dis, data = df_dis, model = "within"), data = df_dis)

```
